The serious gap laying on healthcare system in Thailand^[Code and data are available at: https://github.com/SANGWOONG-LEE/Thailand_Healthcare]

### 2022-04-02 outputs/paper/paper.Rmd

```{r}
#ggplot(data[1:2,], aes(x = Variable, y = Health_Record)) + geom_bar(stat='identity') + facet_wrap(~Mothers_Report)
urban_rural %>%
  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```
```{r}
#ggplot(data[3:7,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
region %>%
  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```
```{r}
#ggplot(data[8:11,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
education %>%
  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```
```{r}
#ggplot(data[12:13,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
religion %>%
  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```
Talk more about it.

Also bills and their average (Figure \@ref(fig:billssssss)). (Notice how you can change the height and width so they don't take the whole page?)

>>>>

```{r fig1,echo=FALSE, fig.cap = "Immunization cases between communities"}
#ggplot(data[1:2,], aes(x = Variable, y = Health_Record)) + geom_bar(stat='identity') + facet_wrap(~Mothers_Report)
urban_rural %>%
  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```

```{r fig2,echo=FALSE, fig.cap = "Immunization cases between region"}
#ggplot(data[3:7,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
region %>%
  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```
```{r}
#ggplot(data[8:11,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
education %>%
  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```

```{r fig4,echo=FALSE, fig.cap = "Immunization cases between religion"}
#ggplot(data[12:13,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
religion %>%
  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```
